There and back again: a retrosynthesis tale

### 2019-03-29 papers/retrosynthesis/article.tex
Collecting data on individual runs

\begin{table}[h!]
\caption{Parameters of T11 run.}
  \centering
  \begin{tabular}{p{8.2cm}p{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
    \toprule
    Parameter & Value & Top-1 & Top-3 & Top-5 \\
    \midrule
    Early stopping loss & 0.10864 & & & \\
    Last training loss & 0.11819 & & & \\
    Epoch (early stopping) & 208 & & & \\
    \midrule
    Greedy search (early stopping, epoch 208) & & 32.83 & &\\
    Greedy search (last, epoch 1000) & & 34.75 & & \\
    Greedy (last 10 average, epoch, 991 - 1000) & & 35.57 & & \\
    \midrule
    Beam, T = 1.0 (early) & & 35.57 & 54.14 & 59.13 \\
    Beam, T = 1.3 (early) & & 35.93 & 54.59 & 59.51 \\ 
    \midrule
    Beam, T = 1.0 (last) & &  &  &  \\
    Beam, T = 1.3 (last) & \\ 
    \midrule
    Beam, T = 1.0 (last 10 average) & &  &  &  \\
    Beam, T = 1.3 (last 10 average) & \\ 
    \bottomrule
  \end{tabular}
  \label{tbl:t11}

@@

\begin{table}[h!]
\caption{Parameters of T21 run.}
  \centering
  \begin{tabular}{p{8.2cm}p{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
    \toprule
    Parameter & Value & Top-1 & Top-3 & Top-5 \\
    \midrule
    Last training loss & 0.05108 & & & \\
    \midrule
    Greedy search (last, epoch 1000) & & 38.85 & & \\
    Greedy (last 10 average, epoch, 991 - 1000) & &  & & \\
    \midrule
    Beam, T = 1.0 (last) & & 40.57 &60.19  & 66.77 \\
    Beam, T = 1.3 (last) & & 41.17 & 60.65 &  67.28 \\ 
    \midrule
    Beam, T = 1.0 (last 10 average) & &  &  &  \\
    Beam, T = 1.3 (last 10 average) & &  &  &  \\ 
    \bottomrule
  \end{tabular}
  \label{tbl:t11}

@@

\begin{table}[h!]
\caption{Parameters of T22 run.}
  \centering
  \begin{tabular}{p{8.2cm}p{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
    \toprule
    Parameter & Value & Top-1 & Top-3 & Top-5 \\
    \midrule
    Last training loss & 0.04943 & & & \\
    \midrule
    Greedy search (last, epoch 996) & &  & & \\
    Greedy (last 10 average, epoch, 991 - 1000) & &  & & \\
    \midrule
    Beam, T = 1.0 (last) & &  &  &  \\
    Beam, T = 1.3 (last) & &  &  &   \\ 
    \midrule
    Beam, T = 1.0 (last 10 average) & &  &  &  \\
    Beam, T = 1.3 (last 10 average) & &  &  &  \\ 
    \bottomrule
  \end{tabular}
  \label{tbl:t11}

>>>>

\begin{table}[h!]
\caption{Parameters of T11 run.}
  \centering
  \begin{tabular}{p{8.2cm}p{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
    \toprule
    Parameter & Value & Top-1 & Top-3 & Top-5 \\
    \midrule
    Early stopping loss & 0.10864 & & & \\
    Last training loss & 0.11819 & & & \\
    Epoch (early stopping) & 208 & & & \\
    \midrule
    Greedy search (early stopping, epoch 208) & & 32.83 & &\\
    Greedy search (last, epoch 1000) & & 34.75 & & \\
    Greedy (last 10 average, epoch, 991 - 1000) & & 35.57 & & \\
    \midrule
    Beam, T = 1.0 (early) & & 35.57 & 54.14 & 59.13 \\
    Beam, T = 1.3 (early) & & 35.93 & 54.59 & 59.51 \\ 
    \midrule
    Beam, T = 1.0 (last) & & 37.15 & 55.22 &  60.49 \\
    Beam, T = 1.3 (last) & & 37.67 & 55.97 & 61.01 \\ 
    \midrule
    Beam, T = 1.0 (last 10 average) & & 37.83 & 56.08 &  60.63 \\
    Beam, T = 1.3 (last 10 average) & & 38.15 & 56.71 & 61.31 \\ 
    \bottomrule
  \end{tabular}
  \label{tbl:t11}

\subsubsection{Model 1 (run-101)}

\begin{figure}[h!]
  \centering
  \includegraphics[width = 16.5cm]{images/t12.pdf}
  \caption{Learning curves and rate schedule for T1 model. Losses for training and validation datasets on the left, usual learning rate schedule on the right.}
  \label{fig:t11}
\end{figure}

\begin{table}[h!]
\caption{Parameters of T12 run.}
  \centering
  \begin{tabular}{p{8.2cm}p{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
    \toprule
    Parameter & Value & Top-1 & Top-3 & Top-5 \\
    \midrule
    Early stopping loss & 0.09926 & & & \\
    Last training loss & 0.04832 & & & \\
    Epoch (early stopping) & 162 & & & \\
    \midrule
    Greedy search (early stopping, epoch 162) &  &  & &\\
    Greedy search (last, epoch 990) &  &  & & \\
    Greedy (last 10 average, epoch, 990 - 999) & &  & & \\
    \midrule
    Beam, T = 1.0 (early) & &  &  &  \\
    Beam, T = 1.3 (early) & &  &  &  \\ 
    \midrule
    Beam, T = 1.0 (last) & &  &  &   \\
    Beam, T = 1.3 (last) & &  &  &  \\ 
    \midrule
    Beam, T = 1.0 (last 10 average) & &  &  &   \\
    Beam, T = 1.3 (last 10 average) & &  &  &  \\ 
    \bottomrule
  \end{tabular}
  \label{tbl:t12}

\subsubsection{Model 1 (run-102)}

\begin{figure}[h!]
  \centering
  \includegraphics[width = 16.5cm]{images/t1-3.pdf}
  \caption{Learning curves and rate schedule for T1 model. Losses for training and validation datasets on the left, usual learning rate schedule on the right.}
  \label{fig:t11}
\end{figure}

\begin{table}[h!]
\caption{Parameters of T13 run.}
  \centering
  \begin{tabular}{p{8.2cm}p{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
    \toprule
    Parameter & Value & Top-1 & Top-3 & Top-5 \\
    \midrule
    Early stopping loss &  & & & \\
    Last training loss &  & & & \\
    Epoch (early stopping) & 193 & & & \\
    \midrule
    Greedy search (early stopping, epoch 193) &  &  & &\\
    Greedy search (last, epoch 990) &  &  & & \\
    Greedy (last 10 average, epoch, 990 - 999) & &  & & \\
    \midrule
    Beam, T = 1.0 (early) & &  &  &  \\
    Beam, T = 1.3 (early) & &  &  &  \\ 
    \midrule
    Beam, T = 1.0 (last) & &  &  &   \\
    Beam, T = 1.3 (last) & &  &  &  \\ 
    \midrule
    Beam, T = 1.0 (last 10 average) & &  &  &   \\
    Beam, T = 1.3 (last 10 average) & &  &  &  \\ 
    \bottomrule
  \end{tabular}
  \label{tbl:t12}

@@

\begin{table}[h!]
\caption{Parameters of T21 run.}
  \centering
  \begin{tabular}{p{8.2cm}p{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
    \toprule
    Parameter & Value & Top-1 & Top-3 & Top-5 \\
    \midrule
    Last training loss & 0.05108 & & & \\
    \midrule
    Greedy search (last, epoch 1000) & & 38.85 & & \\
    Greedy (last 10 average, epoch, 991 - 1000) & & 39.25 & & \\
    \midrule
    Beam, T = 1.0 (last) & & 40.57 &60.19  & 66.77 \\
    Beam, T = 1.3 (last) & & 41.17 & 60.65 &  67.28 \\ 
    \midrule
    Beam, T = 1.0 (last 10 average) & & 40.98 & 60.29 & 67.00 \\
    Beam, T = 1.3 (last 10 average) & &  41.61 & 60.85 & 67.37 \\ 
    \bottomrule
  \end{tabular}
  \label{tbl:t11}

@@

\begin{table}[h!]
\caption{Parameters of T22 run.}
  \centering
  \begin{tabular}{p{8.2cm}p{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
    \toprule
    Parameter & Value & Top-1 & Top-3 & Top-5 \\
    \midrule
    Last training loss & 0.04943 & & & \\
    \midrule
    Greedy search (last, epoch 996) & & 38.79 & & \\
    Greedy (last 10 average, epoch, 991 - 1000) & & 39.11 & & \\
    \midrule
    Beam, T = 1.0 (last) & & 40.98 & 60.39 & 66.38  \\
    Beam, T = 1.3 (last) & & 41.58 &  61.21 & 66.94 \\ 
    \midrule
    Beam, T = 1.0 (last 10 average) & & 41.14  & 60.59 &  66.41\\
    Beam, T = 1.3 (last 10 average) & &  41.87 &  61.35 &  67.08\\ 
    \bottomrule
  \end{tabular}
  \label{tbl:t11}

\newpage
 \subsubsection{Model 2 (run-202)}

\begin{figure}[h!]
  \centering
  \includegraphics[width = 16.5cm]{images/t2-3.pdf}
  \caption{Learning curves and rate schedule for T2 model. Loss for training on the left, usual learning rate schedule on the right.}
  \label{fig:t21}
\end{figure}

\begin{table}[h!]
\caption{Parameters of T23 run.}
  \centering
  \begin{tabular}{p{8.2cm}p{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
    \toprule
    Parameter & Value & Top-1 & Top-3 & Top-5 \\
    \midrule
    Last training loss &  & & & \\
    \midrule
    Greedy search (last, epoch 984) & & 0.04826 & & \\
    Greedy (last 10 average, epoch, 991 - 1000) & &  & & \\
    \midrule
    Beam, T = 1.0 (last) & &  &  &   \\
    Beam, T = 1.3 (last) & &  &   &  \\ 
    \midrule
    Beam, T = 1.0 (last 10 average) & &   &  &  \\
    Beam, T = 1.3 (last 10 average) & &   &   &  \\ 
    \bottomrule
  \end{tabular}
  \label{tbl:t11}
